### 2021-05-03 architecture.tex
Use only expandable glossary commands in section titles
as recommended by glossaries user manual.
Restore the LLNCS formatting of subsubsections

\subsection{Graph constructor: From \gls{cnf} to graphs}
\label{sec:graphifier}

@@

\subsection{\Gls{gcn}: From graphs to symbol embeddings}
\label{sec:gcn}

@@

\subsection{Output layer: From symbol embeddings to symbol costs}
\label{sec:output}
% Terminology: Deep Learning Book

@@

\subsection{Sort: From symbol costs to precedence}
\label{sec:sorting}

@@

\section{Training procedure}
\label{sec:training}

@@

\subsection{Precedence cost}

@@

\subsection{Learning to rank precedences}
\label{sec:ranking}

@@

\subsubsection{Training data}

@@

\subsubsection{Loss function}

>>>>

\subsection{\titlecap{Graph constructor: From \glsentryshort{cnf} to graphs}}
\label{sec:graphifier}

@@

\subsection{\titlecap{\glsentryshort{gcn}: From graphs to symbol embeddings}}
\label{sec:gcn}

@@

\subsection{\titlecap{Output layer: From symbol embeddings to symbol costs}}
\label{sec:output}
% Terminology: Deep Learning Book

@@

\subsection{\titlecap{Sort: From symbol costs to precedence}}
\label{sec:sorting}

@@

\section{\titlecap{Training procedure}}
\label{sec:training}

@@

\subsection{\titlecap{Precedence cost}}

@@

\subsection{\titlecap{Learning to rank precedences}}
\label{sec:ranking}

@@

\subsubsection{\titlecap{Training data}.}

@@

\subsubsection{\titlecap{Loss function}.}
